### 2014-03-11 Docs/getting_started/getting_started.tex
update the getting started with some new info

@@

\maestro\ requires the \boxlib\ library to manage the grids and 
parallelization.  We also rely on the build system in \boxlib\ to
build a \maestro\ executable.  \boxlib\ can be obtained via {\tt
git}\footnote{{\tt git} is an open-source source code version control
system.  It is a standard part of any Linux distribution.  You may
need to use your system's package manager to install {\tt git} if it
is not already present} as:
\begin{verbatim}
git clone https://ccse.lbl.gov/pub/Downloads/BoxLib.git
\end{verbatim}

@@

\visit\ is a powerful, DOE-supported visualization tool for 2- and 3D
datasets.  It can do contouring, volume rendering, streamlines, ...\, ,
directly from \boxlib\ plotfiles.   Details on
\visit\ can be found at:\newline
 {\tt https://wci.llnl.gov/codes/visit/home.html}\,. \newline
The easiest way to get started with \visit\ is to download a precompiled
binary from the \visit\ webpage.

@@

>>>>

\item {\em Get a copy of \maestro}.

If you don't already have a copy of \maestro, you can obtain one
via {\tt git}\footnote{{\tt git} is an open-source source code version control
system.  It is a standard part of any Linux distribution.  You may
need to use your system's package manager to install {\tt git} if it
is not already present} as:
\begin{verbatim}
git clone http://bender.astro.sunysb.edu/Maestro/staging/MAESTRO.git
\end{verbatim}
\maestro\ is under active development, so you will want to keep in 
sync with the changes by periodically pulling from the repository.  Simply
type
\begin{verbatim}
git pull
\end{verbatim}
in the {\tt MAESTRO/} directory.

@@

\maestro\ requires the \boxlib\ library to manage the grids and 
parallelization.  We also rely on the build system in \boxlib\ to
build a \maestro\ executable.  \boxlib\ can be obtained via {\tt
git} as:
\begin{verbatim}
git clone https://ccse.lbl.gov/pub/Downloads/BoxLib.git
\end{verbatim}

You will periodic want to update \boxlib\ by doing
\begin{verbatim}
git pull
\end{verbatim}
in the {\tt BoxLib/} directory.

@@

\visit\ is a powerful, DOE-supported visualization tool for 2- and 3D
datasets.  It can do contouring, volume rendering, streamlines, ...\, ,
directly from \boxlib\ plotfiles.   Details on
\visit\ can be found at:\newline
 \url{https://wci.llnl.gov/codes/visit/home.html}\,. \newline
The easiest way to get started with \visit\ is to download a precompiled
binary from the \visit\ webpage.

@@

\subsection{\yt}

\yt\ (version 3.0 and later) can natively read the \maestro\ plotfiles.  See
the \yt\ documentation or \S~\ref{sec:vis:yt}.
